Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Building figure for the mixtures.

---
title: "Extreme Value Chapter"
author: "Javiera Rudolph"
output:
  html_document:
    toc: yes
    self_contained: false
---

@@

# Figure 1

@@

```{r fig.width=12, fig.height=8}
desired_means <- c(28, 32, 40, 50)
desired_sds <- c(49.7, 39.9, 33.3, 31.1)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
# These are the weights for the distribution
pis <- c( 0.1, 0.2, 0.3, 0.4)

@@

# Build the densities for plotting
weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=pis[y]*5, alpha = 0.8))

# Plot density components of the mixture
ggplot() +
  weighted_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) -> densities_plot
# densities_plot

# Plot the means and sd for each of the curves
data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
  mutate(lo = desired_means - desired_sds,
         hi = desired_means + desired_sds) %>%
  ggplot(., aes(x = gID, y = desired_means, color = gID)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
  scale_color_manual(values = dens_cols) +
  labs(y = "Mean +/- SD") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") -> means_sd_plot
# means_sd_plot

# Align these plots to have multiple panels lates
top_row <- plot_grid(densities_plot, means_sd_plot, rel_widths = c(2,1))

>>>>

---
title: "Extreme Value Chapter 3"
author: "Javiera Rudolph"
output:
  html_document:
    toc: yes
    self_contained: false
---

@@

# Figure 1 - the mixture scenarios considered

@@

```{r Mixtures_FX}
# Figure 1 function to make multiples

mixtures_plot_fx <- function(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds, weighted = FALSE){

  if(weighted == TRUE){
    lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=pis[y]*5, alpha = 0.8))
  } else{
    lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=1, alpha = 0.8))
  }

  # Plot density components of the mixture
  ggplot() +
    lnorm_densities +
    theme_minimal(base_size = 6) +
    labs(y = "Density") +
    lims(x = c(0, 150)) -> densities_plot
  # densities_plot

  # Plot the means and sd for each of the curves
  data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
    mutate(lo = desired_means - desired_sds,
           hi = desired_means + desired_sds) %>%
    ggplot(., aes(x = gID, y = desired_means, color = gID)) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
    scale_color_manual(values = dens_cols) +
    labs(y = "Mean +/- SD") +
    theme_minimal(base_size = 6) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          legend.position = "none") -> means_sd_plot
  # means_sd_plot

  # Align these plots to have multiple panels lates
  plot_grid(NULL, means_sd_plot, densities_plot, rel_widths = c(0.1, 1, 3), nrow = 1)
}

```{r fig.width=4, fig.height=5}
# Scenarios:
pis <- c( 0.1, 0.2, 0.3, 0.4)
dens_cols <- pal_mixture

# SAME SD INCREASING MEAN ------------------------------
desired_means <- c(30, 40, 50, 60)
desired_sds <- c(25, 25, 25, 25)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A1 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

# SAME MEAN INCREASING SD ------------------------------
desired_means <- c(30, 30, 30, 30)
desired_sds <- c(20, 30, 40, 50)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A2 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

# INCREASING SD INCREASING MEAN ------------------------------
desired_means <- c(30, 40, 50, 60)
desired_sds <- c(20, 30, 40, 50)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A3 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

# DECREASING BOTH ------------------------------
desired_means <- c(60, 50, 40, 30)
desired_sds <- c(50, 40, 30, 20)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A4 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

#INCREASING MEANS DECRESING SD --------------------------------------
desired_means <- c(30, 35, 40, 50)
desired_sds <- c(50, 40, 35, 30)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)

A5 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
ggsave("Ch3_samplesize/Figures/Figure1.png")
```

```{r}
desired_means <- c(28, 32, 40, 50)
desired_sds <- c(49.7, 39.9, 33.3, 31.1)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
# These are the weights for the distribution
pis <- c( 0.1, 0.2, 0.3, 0.4)

@@

top_row <- fig1_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
